### 2012-06-26 inst/examples/logistic_lognormal.Rmd
running bh+uniform and logistic+lognormal

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`

@@

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * true_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * true_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * true_i

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_lognormal/", verbose=TRUE or`

@@

  z_g <- function() rlnorm(1,0, policy_g)
  z_m <- function() rlnorm(1,0, policy_m)
  z_i <- function() rlnorm(1,0,policy_i)

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e5)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

  z_g <- function() rlnorm(1,0, true_g)
  z_m <- function() rlnorm(1,0, true_m)
  z_i <- function() rlnorm(1,0, true_i)
